% Include a header paragraph specific to your product here. Maintenance and support requirements address items specific to the ongoing maintenance and support of your product after delivery. Think of these requirements as if you were the ones who would be responsible for caring for customers/end user after the product is delivered in its final form and in use "in the field". What would you require to do this job? Specify items such as: where, how and who must be able to maintain the product to correct errors, hardware failures, etc.; required support/troubleshooting manuals/guides; availability/documentation of source code; related technical documentation that must be available for maintainers; specific/unique tools required for maintenance; specific software/environment required for maintenance; etc.

% \subsection{Requirement Name}
% \subsubsection{Description}
% Detailed requirement description...
% \subsubsection{Source}
% Source
% \subsubsection{Constraints}
% Detailed description of applicable constraints...
% \subsubsection{Standards}
% List of applicable standards
% \subsubsection{Priority}
% Priority

After the delivery of our checkers-playing program for the UR5 robotic arm, the customer will need to maintain the hardware and software in case our product were to ever fail. Since we will be using Commercial Off The Shelf components such as the UR5 robotic arm itself, we will include official documents for those components along with our own source code, documentation, and contact information.

\subsection{The product source code documentation will be available.}
\subsubsection{Description}
Documentation for the source code will be accessible for the customer in case of technical issues or modifications needed.
\subsubsection{Source}
Hoang Ho
\subsubsection{Constraints}
Most of the programming done for the robot arm's movements may be done on the UR5 controller box interface. The programs made here may not be able to be exported.
\subsubsection{Standards}
N/A
\subsubsection{Priority}
High

\subsection{The official UR5 user manual will be available.}
\subsubsection{Description}
The official user manual for the UR5 robot arm will be provided to the customer.
\subsubsection{Source}
Hoang Ho
\subsubsection{Constraints}
N/A
\subsubsection{Standards}
N/A
\subsubsection{Priority}
High