The following listed items are the projected constraints imposed on the checkers playing UR5 co-bot arm project:

\begin{itemize}
    \item The final prototype demonstration must be completed by May 1st, 2022.
    \item Total development costs for tools, hardware components, and 3D printing must not exceed \$800.
    \item The UR5 co-bot is located at a specific site, so access to it may be restricted by certain business hours. Additionally, programming and testing for robot is less flexible.
    \item Team members have minimal knowledge with computer vision and mechanical components, such as cameras, sensors, and grippers.
    \item Depending on the gripper type for the co-bot arm, a customized checkers board and pieces will have to be created.
    \item There is one co-bot arm for all members to work with.
    \item The UR5 co-bot may need specific lighting in the area that the checkers game is being played in order to adequately detect the pieces. 
    
\end{itemize}

% commented out the instructions using iffalse and fi
\iffalse
Constraints are limitations imposed on the project, such as the limitation of cost, schedule, or resources, and you have to work within the boundaries restricted by these constraints. All projects have constraints, which are defined and identified at the beginning of the project.

Constraints are outside of your control. They are imposed upon you by your client, organization, government regulations, availability of resources, etc. Occasionally, identified constraints turn out to be false. This is often beneficial to the development team, since it removes items that could potentially affect progress.

This section should contain a list of at least 5 of the most critical constraints related to your project. For example:

The following list contains key constraints related to the implementation and testing of the project.

\begin{itemize}
  \item Final prototype demonstration must be completed by May 1st, 20XX
  \item The customer will provide no more than two maintenance personnel to assist in on-site installation
  \item Customer installation site will only be accessible by development team during normal business hours
  \item Total development costs must not exceed \$800
  \item All data obtained from customer site must be reviewed and approved for release by the Information Security Office prior to being copied to any internet connected storage medium
\end{itemize}
\fi